:::: {#fig-tid layout-ncol=2 layout-nrow=2}
::: {#fig-tid1}
```{r}
#| fig-height: 7
#| fig-width: 9
timefunc()
```     
`{r} paste0(startyeartmp, "-", global_year)`
:::
::: {#fig-tid2}
```{r}
#| fig-height: 7
#| fig-width: 9
barsummary(unit = c("Hospital", "Primary care"))
```     
`{r} paste0(global_year - 2, "-", global_year, ", Sweden")`
:::
::: {#fig-tid3}
```{r}
#| fig-height: 7
#| fig-width: 9
barsummary(unit = "Hospital")
```     
`{r} paste0(global_year - 2, "-", global_year, ", Hospital")`
:::
::: {#fig-tid4}
```{r}
#| fig-height: 7
#| fig-width: 9
barsummary(unit = "Primary care")
```     
`{r} paste0(global_year - 2, "-", global_year, ", Primary care")`
:::
`{r} paste0("Trends in ", qinametmp)`
::::


:::: {#fig-region layout-ncol=2 layout-nrow=2}
::: {#fig-region1}
```{r}
#| fig-height: 8
#| fig-width: 7
qifunc(type = "Index", unit = "region")
```     
Index
:::
::: {#fig-region2}
```{r}
#| fig-height: 8
#| fig-width: 7
qifunc(type = "1-80 days follow-up", unit = "region")
```     
1-80 days follow-up
:::
::: {#fig-region3}
```{r}
#| fig-height: 8
#| fig-width: 7
qifunc(type = "1 year follow-up", unit = "region")
```     
1 year follow-up
:::
::: {#fig-region4}
```{r}
#| fig-height: 8
#| fig-width: 7
qifunc(type = "2+ year follow-up", unit = "region")
```     
2+ year follow-up
:::
`{r} paste0(firstcap(qinametmp), " by region, ", global_year)`
::::


:::: {#fig-centre layout-ncol=2 layout-nrow=2}
::: {#fig-centre1}
```{r}
#| fig-height: 8
#| fig-width: 7
qifunc(type = "Index")
```     
Index
:::
::: {#fig-centre2}
```{r}
#| fig-height: 8
#| fig-width: 7
qifunc(type = "1-80 days follow-up")
```     
1-80 days follow-up
:::
::: {#fig-centre3}
```{r}
#| fig-height: 8
#| fig-width: 7
qifunc(type = "1 year follow-up")
```     
1 year follow-up
:::
::: {#fig-centre4}
```{r}
#| fig-height: 8
#| fig-width: 7
qifunc(type = "2+ year follow-up")
```     
2+ year follow-up
:::
`{r} paste0(firstcap(qinametmp), " by centre, ", global_year)`
::::
